Ants-Review: a Protocol for Open Anonymous Peer Reviews

### 2020-09-25 paper-v1.tex
Last fixes before submission.

\newline Partnering with publishers, the startup \emph{Publons}\footnote[1]{\emph{Publons}. https://publons.com} provides a free metric service for tracking, verification and recognition of publications, peer-reviews and journal editing in a single researcher identifier that showcases a record of scientific activity and impact based on authors' productivity.

@@

\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflicts of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data immutability and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remains unaltered and indelible. This notarization process is called Proof of Existence (PoE) and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s externally owned accounts (EOA) addresses and Zero-Knowledge Proof, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).

@@

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\small{
\caption{Exagones represent the protocol's smart contracts. Ellipse represents the smart contract inherited by AntsReview. Clouds represent integrations into the protocol. Rectangles represent smart contracts' libraries.
\textbf{a} Core contract of the protocol implementing a bounty system with the functions listed.
\textbf{b} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
\textbf{c} Native token used in the protocol. It is linked to (\textbf{a}), (\textbf{e}) and to (\textbf{d}).
\textbf{d} Faucet to distribute \emph{ANTS} on Kovan Testnet for testing purposes. 
\textbf{e} Integration with Aztec Protocol to wrap (\textbf{c}) into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview (\textbf{a}).
\textbf{g} Integration with ERC20 tokens like \emph{Dai}, and De-Fi services like MakerDAO DSR to be used in the protocol.
\textbf{h} Library used by the protocol for secure contract development with the modules listed.}}
\label{fig:contracts}
\end{figure}

@@

\subsubsection{Privacy.}
The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent, and via private transactions allowed by AZTEC\cite{AZTEC} Protocol's security layer.

\paragraph{\textbf{Pseudo-anonymity.}}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan \footnote[11]{\emph{Etherscan}. https://etherscan.io/.}) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{\textbf{Private transactions.}}AZTEC Protocol was conceived to enable privacy on public blockchains. It uses zero-knowledge Succinct Non-Interactive Argument of Knowledge (zk-SNARKs) \cite{zSNARK} and homomorphic encryption \cite{HomEncr} to validate encrypted transactions. zk-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier. zk-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents. Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}, 
a universal zk-SNARK construction that reduces gas costs and improves scalability.

\subsubsection{Tokenomics.}
Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}. https://eips.ethereum.org/EIPS/eip-20.} tokens, each of whom plays an integral role in the functioning and anonymity of the decentralized protocol. ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview. It's implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
A Faucet (see Figure \ref{fig:contracts}, (\text{d}) is implemented to distribute ANTS token on Kovan Testnet for testing purposes. zkANTS (see Figure \ref{fig:contracts}, (\textbf{e})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents of the protocol, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters. It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}. https://github.com/ethereum/EIPs/issues/1724.} will be used as a template to build an AZTEC-compatible asset.
\\
\\ The current state of the art of Ants-Review is represented by version 0.2.0 (MVP) live on Ethereum Kovan Testnet (see Supplementary Material).

\section{Discussions}
We have described how Ants-Review protocol can solve the limitations of the current peer review system (see 2.1). In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see §AntsReview in 3.2); the social and cognitive biases via anonymity granted by AZTEC Protocol (see §Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers through the creation of the community of Anters. 
\subsection{Future developments}
An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}. https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation}. Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[15]{\emph{Pot}. https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[16]{\emph{Compound}. https://compound.finance}, to cite a few.
Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
A Decentralized Autonomous Organization (DAO) \cite{Wang-DAO,DAOContr} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
\newline Finally, a protocol upgrade inspired by \emph{Discover}\footnote[17]{\emph{Discover.sol}. https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol}, a Web3 browser by \emph{Status}\footnote[18]{\emph{Status}. https://status.im/} and still under investigation would allow Anters to validate peer reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer reviews.

\subsection{A new community-driven standard?}
As Tennant points out \cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}). Recently, pre-print servers, such as \emph{arXiv} and \emph{biorXiv}, started integrating peer-review services into their platforms: \emph{PREreview}\footnote[19]{\emph{PREreview.} https://www.prereview.org}, \emph{PeerCommunityIn.}\footnote[20]{\emph{PeerCommunityIn} https://peercommunityin.org}, \emph{Review Commons}\footnote[21]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review}\footnote[22]{\emph{PrePrint Review.} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}. This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer review platforms and justify their added value (\emph{ibidem}). In our proposal we also decoupled the peer review process from the publishers giving it back to the scientific community and applying incentives from tokenomics. We foresee that the future will evolve towards community-driven peer reviews: peer reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer reviews \cite{UPR}: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)\cite{AIRA}} leaving to the reviewers the sole task of evaluating the content of a paper. Building smart contracts for peer reviews might accelerate this novel process of standardization. We hope that soon the value of peer review as a public good will be recognized by research funders and hiring committees.

>>>>

\newline Partnering with publishers, the startup \emph{Publons}\footnote[1]{\emph{Publons}. https://publons.com} provides a free metric service for tracking, verification and recognition of publications, peer reviews and journal editing in a single researcher identifier that showcases a record of scientific activity and impact based on authors' productivity.

@@

\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflicts of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data immutability and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remains unaltered and indelible. This notarization process is called Proof of Existence (PoE) and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s externally owned accounts (EOA) addresses and zero-knowledge proof, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).

@@

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\small{
\caption{Exagones represent the protocol's smart contracts. Ellipse represents the smart contract inherited by AntsReview. Clouds represent integrations into the protocol. Rectangles represent smart contracts' libraries.
\textbf{a} Core contract of the protocol implementing a bounty system with the functions listed.
\textbf{b} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
\textbf{c} Native token used in the protocol. It is linked to (\textbf{a}), (\textbf{e}) and to (\textbf{d}).
\textbf{d} Faucet to distribute \emph{ANTS} on Kovan Testnet for testing purposes. 
\textbf{e} Integration with Aztec Protocol to wrap (\textbf{c}) into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} Integration with IPFS to upload papers, requirements and peer reviews and store the hash as \emph{PoE} into AntsReview (\textbf{a}).
\textbf{g} Integration with ERC20 tokens like \emph{Dai}, and De-Fi services like MakerDAO DSR to be used in the protocol.
\textbf{h} Library used by the protocol for secure contract development with the modules listed.}}
\label{fig:contracts}
\end{figure}

@@

\subsubsection{Privacy.}
The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent, and via private transactions allowed by AZTEC \cite{AZTEC} Protocol's security layer.

\paragraph{\textbf{Pseudo-anonymity.}}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan \footnote[11]{\emph{Etherscan}. https://etherscan.io/}) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{\textbf{Private transactions.}}AZTEC Protocol was conceived to enable privacy on public blockchains. It uses zero-knowledge Succinct Non-Interactive Argument of Knowledge (zk-SNARKs) \cite{zSNARK} and homomorphic encryption \cite{HomEncr} to validate encrypted transactions. zk-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier; they are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents. Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}, 
a universal zk-SNARK construction that reduces gas costs and improves scalability.

\subsubsection{Tokenomics.}
Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}. https://eips.ethereum.org/EIPS/eip-20} tokens, each of whom plays an integral role in the functioning and anonymity of the decentralized protocol. ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview. It's implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
A Faucet (see Figure \ref{fig:contracts}, (\text{d}) is implemented to distribute ANTS token on Kovan Testnet for testing purposes. zkANTS (see Figure \ref{fig:contracts}, (\textbf{e})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents of the protocol, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters. It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}. https://github.com/ethereum/EIPs/issues/1724} will be used as a template to build an AZTEC-compatible asset.
\\
\\ The current state of the art of Ants-Review is represented by version 0.2.0 (MVP) live on Ethereum Kovan Testnet (see Supplementary Material).

\section{Discussions}
We have described how Ants-Review protocol can solve the limitations of the current peer review system (see 2.1). In particular, the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see §AntsReview in 3.2); the social and cognitive biases can be counteracted via anonymity granted by AZTEC Protocol (see §Privacy in 3.2); the slowness of the process, the need for evaluation of the peer reviews themselves and the need for increasing the number of reviewers can be worked out through the creation of the community of Anters. 
\subsection{Future developments}
An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}. https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation}. Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[15]{\emph{Pot}. https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[16]{\emph{Compound}. https://compound.finance}, to cite a few.
Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
A Decentralized Autonomous Organization (DAO) \cite{Wang-DAO,DAOContr} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
\newline Finally, a protocol upgrade inspired by \emph{Discover}\footnote[17]{\emph{Discover.sol}. https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol}, a Web3 browser by \emph{Status}\footnote[18]{\emph{Status}. https://status.im/} and still under investigation would allow Anters to validate peer reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer reviews.

\subsection{A new community-driven standard?}
As Tennant points out \cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}). Recently, pre-print servers, such as \emph{arXiv} and \emph{biorXiv}, started integrating peer-review services into their platforms: \emph{PREreview}\footnote[19]{\emph{PREreview.} https://www.prereview.org}, \emph{PeerCommunityIn}\footnote[20]{\emph{PeerCommunityIn} https://peercommunityin.org}, \emph{Review Commons}\footnote[21]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review}\footnote[22]{\emph{PrePrint Review.} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}. This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer review platforms and justify their added value (\emph{ibidem}). In our proposal we also decoupled the peer review process from the publishers giving it back to the scientific community and applying incentives from tokenomics. We foresee that the future will evolve towards community-driven peer reviews: peer reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer reviews \cite{UPR}: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)\cite{AIRA}} leaving to the reviewers the sole task of evaluating the content of a paper. Building smart contracts for peer reviews might accelerate this novel process of standardization. We hope that soon the value of peer review as a public good will be recognized by research funders and hiring committees.
